### 2018-04-01 paper/sexSelectionSpacing-ver1.tex
Edit Does Sex Selection Change within Spells

The predicted sex ratio may change within a spell for, at
least, two reasons.
First, parents may stop using prenatal sex determination within
a spell once the duration from the previous birth becomes long enough.
The desire for short spacing could, for example, arise from 
economies of scale in childbearing and rearing that parents lose 
if children were born too far apart \citep[p 374]{schultz97}. 
In this case we should observe the predicted sex ratio decline
with spell length.

@@

Figures \ref{fig:decreasing_sex_ratio} and \ref{fig:increasing_sex_ratio} show
examples of how sex ratio behave within spells.
Both are for women with eight or more education since the results above indicate
that they are the most likely to use sex selection or other means of achieving 
an unequal sex ratio.
Figure \ref{fig:decreasing_sex_ratio} shows results for the second spell for
the 1995--2004 and 2005--2016 periods for women with a girl as their first
child by area of residence.
Figure \ref{fig:increasing_sex_ratio} shows results for the third spell for
the same two periods for urban women with either two girls or one boy and one
girl as their first two children.%
\footnote{
There is no evidence of unequal sex ratios in either period for similar women 
with two boys as their first two children as shown in Figure TK.
}

Within the second spell, both urban and rural women show a declining
sex ratio as duration increases for the 1995--2004 period, whereas there
is little change, or possibly a small increase, with duration for the 
2005--2016 period.
These results are consistent with a situation where fertility is declining
over time leaving less room for a change in the decision to use sex selection.
Fertility decline is not immediately apparent from the second spell 
results, but the third spell shows that the likelihood of progressing from
two to third children declines by approximately 15 percentage points if
the woman has given birth to a boy.
Furthermore, as the Appendix shows, only about 25\% of urban women with 
two boys have a third child in the 2005--2016 period, 
down from close to 60\% in the 1995--2004 period.

The third spell figures show a very different situation with almost no 
change in sex ratios with duration for women with two girls, but substantial 
increases in sex ratios with duration for women with one boy and one girl.
The high, but stable, sex ratio for women with two girls is likely 
motivated by the combined desire to limit fertility and ensure a son;
similarly to the situation for the second spell as shown in 
Figure \ref{fig:decreasing_sex_ratio} (b) and (d).

The increase in sex ratio with duration for women who already have
given birth to a boy likely illustrates the case where there is a
combination of degrees of son preference.
Say that one group wants one son and after that will not use sex
selection, whereas another group has a strong preference for two
sons (or either have or expect to lose the boy they already have)
and that the two groups conceive at the same rate.
In that case, we should expect exactly the increasing sex ratios
we observe, especially given the declining fertility over time.

>>>>

The predicted sex ratio may change within a spell for, at
least, two reasons.
First, parents may stop using prenatal sex determination within
a spell once the duration from the previous birth becomes long enough.
The desire for short spacing could, for example, arise from 
economies of scale in childbearing and rearing that parents lose 
if children are born too far apart \citep[p 374]{schultz97}. 
In this case, we should observe the predicted sex ratio decline
with spell length.

@@

Figures \ref{fig:decreasing_sex_ratio} and \ref{fig:increasing_sex_ratio} show
examples of how sex ratio behave within spells.
Both are for women with eight or more education since the results above indicate
that they are the most likely to use sex selection or other means of achieving 
an unequal sex ratio.
Figure \ref{fig:decreasing_sex_ratio} shows results for the second spell for
the 1995--2004 and 2005--2016 periods for women with a girl as their first
child by area of residence.
Figure \ref{fig:increasing_sex_ratio} shows results for the third spell for
the same two periods for urban women with either two girls or one boy and one
girl as their first two children.

Within the second spell, both urban and rural women show a declining
sex ratio as duration increases for the 1995--2004 period, whereas there
is little change, or possibly a small increase, with duration for the 
2005--2016 period.
These results are consistent with a situation where fertility is declining
over time leaving less room for a change in the decision to use sex selection.
Fertility decline is not immediately apparent from the second spell 
results, but the third spell shows that the likelihood of progressing from
two to third children declines by approximately 15 percentage points if
the woman has given birth to a boy.

The third spell figures show a very different situation with substantial 
increases in sex ratios.
The high sex ratio for women with two girls is likely 
motivated by the combined desire to limit fertility and ensure a son;
similarly to the situation for the second spell as shown in 
Figure \ref{fig:decreasing_sex_ratio} (b) and (d).

The increase in sex ratio with duration for women who already have
given birth to a boy likely illustrates the case where there is a
combination of degrees of son preference.
Say that one group wants one son and after that will not use sex
selection, whereas another group has a strong preference for two
sons (or either have or expect to lose the boy they already have)
and that the two groups conceive at the same rate.
In that case, we should expect precisely the increasing sex ratios
we observe, especially given the declining fertility over time.
